Data preparation

### 2023-03-08 04. Analysis/scripts/01_data_preparation.Rmd
Update 01_data_preparation.Rmd
Testing other joins

```{r}
prep_base_1 <- files_1[1] %>% 
  map_dfr(~mutate(.data = read_csv(., 
    col_types = cols(Date = col_date(format = "%m_%d_%Y"))), 
        file_name = str_remove(.,pattern = file.path(params$google_drive_home,"03. Data Collection"))
      )) %>% 
  clean_names() %>% 
  distinct() %>% 
  separate(supervisor_name,into = c("sup_last","sup_first"), sep = ",") %>% 
  mutate(
    across(
      .cols = starts_with("sup_"),
      .fns = ~word(.,1)
    )
  ) %>% 
  unite(col = "supervisor_display_name",sup_first,sup_last, sep = " ") %>% 
  rename(file_name_1 =file_name)
```

@@

@@

```{r}
step_1 <- prep_base_1 %>% 
   left_join(prep_base_2_1,
            by = c("employee_name" = "full_name",
                   "sso" = "gsa_sso",
                   "dept_id" = "department_id",
                   "supervisor_display_name" = "supervisor_display_name"
                   )) %>% 
  # filter(rollback(date) == snapshot_date |
  #          rollforward(date) == snapshot_date) %>%
  # select(-snapshot_date, -starts_with("file_name")) %>% 
  distinct()
  # skim()
  # get_dupes(employee_e_mail_address,date)
```

>>>>

```{r}
prep_base_1 <- files_1 %>% 
  map_dfr(~mutate(.data = read_csv(., 
    col_types = cols(Date = col_date(format = "%m_%d_%Y"))), 
        file_name = str_remove(.,pattern = file.path(params$google_drive_home,"03. Data Collection"))
      )) %>% 
  clean_names() %>% 
  distinct() %>% 
  separate(supervisor_name,into = c("sup_last","sup_first"), sep = ",") %>% 
  mutate(
    across(
      .cols = starts_with("sup_"),
      .fns = ~word(.,1)
    )
  ) %>% 
  unite(col = "supervisor_display_name",sup_first,sup_last, sep = " ") %>% 
  rename(file_name_1 =file_name)%>% 
  mutate(
    date_month = floor_date(date,unit = "month"),
    date_month_rollback = rollback(date_month),
    date_month_forward = rollforward(date_month)
  )
```

@@

```{r}
prep_base_2 <- files_2 %>% 
  map_dfr(~mutate(.data = read_xlsx(path = ., 
                                    col_types = c("date", "text", "text", 
        "text", "text", "text", "text", "text", 
        "text", "date", "text", "text", "text", 
        "text", "text", "text", "text", "text", 
        "text", "text", "text", "text", "text", 
        "text", "text", "text", "text", "text")), 
        file_name = str_remove(.,pattern = file.path(params$google_drive_home,"03. Data Collection"))
      )) %>% 
  clean_names() %>% 
  distinct() %>% 
  mutate(
    across(
      .cols = where(is.POSIXct),
      .fns = ~as_date(.)
    )
  )
```

```{r}
step_1 <- prep_base_1 %>% 
  inner_join(prep_base_2,
            by =  c("employee_name" = "full_name"),
            suffix = c("_daily","_roster")
  ) %>% 
  select(-starts_with("file_name")) %>% 
  distinct() %>% 
  filter(supervisor_display_name_daily == supervisor_display_name_roster) %>%
  filter(dept_id == department_id) %>%
  filter(date_month_rollback == snapshot_date)
```

```{r}
step_1 %>%
  get_dupes(date,employee_e_mail_address) %>%
  arrange(desc(dupe_count))
```

```{r}
step_2 <- 
  prep_base_1 %>% 
  anti_join(step_1) %>% 
  inner_join(prep_base_2,
            by =  c("employee_name" = "full_name"),
            suffix = c("_daily","_roster")
  ) %>% 
  select(-starts_with("file_name")) %>% 
  distinct() %>% 
  filter(supervisor_display_name_daily == supervisor_display_name_roster) %>%
  filter(dept_id == department_id) %>%
  filter(date_month_forward == snapshot_date)
```

```{r}
prep_base_1 %>% 
  anti_join(step_1) %>%
  anti_join(step_2) %>% 
  inner_join(prep_base_2,
            by =  c("employee_name" = "full_name"),
            suffix = c("_daily","_roster")
  ) %>% 
  select(-starts_with("file_name")) %>% 
  distinct() %>% 
  filter(supervisor_display_name_daily == supervisor_display_name_roster) %>%
  filter(dept_id == department_id) %>% 
  select(-snapshot_date) %>% 
  distinct()
```

@@

```{r}
step_1 <- prep_base_1 %>% 
  # select(employee_name) %>% 
  # distinct() %>% 
   left_join(prep_base_2_1,
            by = c("employee_name" = "full_name",
                   "sso" = "gsa_sso",
                   "dept_id" = "department_id",
                   "supervisor_display_name" = "supervisor_display_name"
                   )) %>% 
  # filter(rollback(date) == snapshot_date |
  #          rollforward(date) == snapshot_date) %>%
  # select(-snapshot_date, -starts_with("file_name")) %>% 
  distinct()
  # skim()
  # get_dupes(employee_e_mail_address,date)
```

```{r}
step_1 %>% 
  filter(!is.na(employee_e_mail_address)) %>% 
  get_dupes(employee_name,date,sso, dept_id, supervisor_display_name)
```

```{r}
step_1 %>% 
  filter(!is.na(employee_e_mail_address)) %>% 
  get_dupes(employee_e_mail_address,date)
```

```{r}
step_2 <- 
  step_1 %>% 
  filter(!is.na(employee_e_mail_address)) %>% 
  get_dupes(employee_name) %>% 
  select(employee_name) %>% 
  distinct()
```

```{r}
step_3 <- 
  step_2 %>% 
  inner_join(prep_base_1 %>% 
  select(employee_name,sso) %>% 
    distinct()) %>% 
  left_join(prep_base_2_1,
            by = c("employee_name" = "full_name",
                   "sso" = "gsa_sso"
                   # ,
                   # "dept_id" = "department_id",
                   # "supervisor_display_name" = "supervisor_display_name"
                   )) %>% 
  # filter(rollback(date) == snapshot_date |
  #          rollforward(date) == snapshot_date) %>%
  # select(-snapshot_date, -starts_with("file_name")) %>% 
  distinct()
```

```{r}
step_3 %>% 
  filter(!is.na(employee_e_mail_address)) %>% 
  get_dupes(employee_name,employee_e_mail_address)
```
